%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  %  \cventry
  %    {Assistant Engineer} % Job title
  %    {PT. Cardno Indonesia / Asian Development Bank} % Organization
  %    {Jakarta, Indonesia} % Location
  %    {Dec 2016 - Jul 2017} % Date(s)
  %    {
  %      \begin{cvitems} % Description(s) of tasks/responsibilities
  %        \item {Learnt Geographical Information System (GIS) and generated thematic maps of different ports based on its hinterland potential.}
  %        \item {Synthesised data from various sources, did a spreadsheet analysis and write-up according to requirements set by expert engineers.}
  %      \end{cvitems}
  %    }

  %---------------------------------------------------------
  \cventry
  {Software Engineering Intern (Global APAC Banking Team: Ruby, proto3)} % Job title
  {Stripe Inc.} % Organization
  {Singapore} % Location
  {May 2020 - July 2020} % Date(s)
  {
    \begin{cvitems}
      \item {Built \textbf{an integration with a new payment method} and decoupled my team's services so that they can be \textbf{deployed safely and independently}.}
      \item {\textbf{Saved the company up to hundreds of eng-hours/month} by speeding up scripts runtime along with contribution to Sorbet (\url{https://sorbet.org/}).}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Engineering Intern (Security Team: Python, TypeScript/JavaScript, AWS)} % Job title
  {Asana Inc.} % Organization
  {San Francisco} % Location
  {January 2020 - April 2020} % Date(s)
  {
    \begin{cvitems}
      \item {Smoothly \textbf{ported over existing services to AWS Lambda} for more granular permissions and to run risky software on a separate infrastructure to mitigate potential impact of security breaches, including Asana's image thumbnailing, video snippet creation, and webhook services.}
      \item {Created \textbf{a data pipeline to easily query and audit logs} of engineers access to production machines.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Engineering Intern (Machine Learning Infrastructure Team: Scala, Spark, React, Flow/JavaScript)} % Job title
  {Stripe Inc.} % Organization
  {San Francisco} % Location
  {May 2019 - August 2019} % Date(s)
  {
    \begin{cvitems}
      \item {Built \textbf{an explorable catalog of machine learning features} to help Machine Learning teams better leverage existing features for new models.}
      \item {The catalogue includes visualization of the DAG (Directed Acyclic Graph) of the data transformation used to calculate the feature, sample data and aggregate metrics such as approximate heavy hitters (calculated using SpaceSaver algorithm).}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {iOS Software Engineering Intern (iOS Team: Swift, Objective-C, Functional Reactive Programming)} % Job title
  {Garena Online Pte. Ltd.} % Organization
  {Singapore} % Location
  {May 2018 - Aug 2018} % Date(s)
  {
    \begin{cvitems}
      \item {Developed \textbf{Chainsaw LogViewer}, an iOS file viewer app capable of handling 200k lines, extracting ZIP files, syntax highlighting, regex searching, and is integrated with the debugging menu of my team's product. (App Store link: \url{https://itunes.apple.com/app/id1423011730})}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Teaching Assistant} % Job title
  {National University of Singapore} % Organization
  {Singapore} % Location
  {Aug 2018 - Apr 2020} % Date(s)
  {
    \begin{cvitems}
      \item {Preparing materials and teaching tutorials for undergraduate students, achieving feedback scores above the Faculty average.}
      \item {Courses: CS1101S (SICP), CS2100 (Computer Architecture), CS3210 (Parallel Programming), CS3217 (Software Engineering, iOS Platform)}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Backend Architect and Team Lead (Elixir, Phoenix, Ecto, AWS)} % Job title
  {Source Academy \textmd{\em\tiny(\url{https://github.com/source-academy/cadet/})}} % Organization
  {Singapore} % Location
  {May 2018 - May 2019} % Date(s)
  {
    \begin{cvitems}
      \item {Managed a team of 4 people developing a scalable back-end of Source Academy, the course management website for NUS CS1101S course}
      \item {Designed the overall architecture of the system, including the database schema and API with input from the front-end team.}
    \end{cvitems}
  }

\end{cventries}
